The journey of Multiple Sequence Alignment

### 2021-08-02 MSA_Notum_journey.Rmd
search the profile

# hmmmbuild
```{bash}
hmmbuild --amino --cpu 4  my_data/NOTUM_try my_data/hmmsearch_env_coord_msa_muscle.fa 
hmmbuild --amino --cpu 4  my_data/WIF_try my_data/WIF_hmmsearch_env_coord_msa_muscle.fa 
hmmbuild --amino --cpu 4  my_data/wnt_try my_data/wnt_hmmsearch_env_coord_msa_muscle.fa

>>>>

# hmmbuild
```{bash}
hmmbuild --amino --cpu 4  my_data/NOTUM_try my_data/hmmsearch_env_coord_msa_muscle.fa 
hmmbuild --amino --cpu 4  my_data/WIF_try my_data/WIF_hmmsearch_env_coord_msa_muscle.fa 
hmmbuild --amino --cpu 4  my_data/wnt_try my_data/wnt_hmmsearch_env_coord_msa_muscle.fa 
```

```{bash}
hmmsearch --cut_ga --domtblout my_data/hmm_search/NOTUM_profile_domtbl.out my_data/NOTUM_try my_data/pfam/Pfam-A.fasta > /dev/null
```
